---
title: "H2_JackFriedman"
output: html_document
---

1. Identify a column in your data that *should* be a factor (whether it is or not). Check to see whether R is already treating it as a factor, and if not, convert it into a factor.

```{r}

vdem.full <- read.csv("~/Desktop/PSYC798W/Data/V-Dem-CY-Core-v8.csv")
vdem.sub3 <- subset(vdem.sub1, year > 1899 & year < 2001)

typeof(vdem.full)

lapply(vdem.full[,1:10], class)

class(vdem.full$v2x_polyarchy)

```

2. What are the levels of the factor? How many occurrences of each level are there in the data?
   
```{r}
levels(vdem.full$country_id)

library(dplyr)
vdem.full %>% 
  group_by(country_name) %>%
  summarise(no_rows = length(country_name))
```

3. Create a new column that is a numeric "version" of the factor column, using `as.numeric()`. Use `xtabs()` to see how the values of these columns line up.

```{r}

```

4. Create another column that is a copy of the factor column. Now, recode this new column so that the factor levels have new names. 
  (e.g., if you have a factor with levels "A" and "B", you could make a new column that had "condition A" and "condition B" as the level names instead)

```{r}

```

5. Change the order of the levels in your new factor, using three different methods:
  a. `relevel()`
  b. `reorder()`
  c. `factor()`

```{r}

```



